A Multi-Modal Model of Object Deformation under Robotic Pushing

### 2016-12-24 twostagedo-rev-Dec-16.tex
lots of small changes to satisfy reviewer 3.

\begin{figure}[!t]
\centering\includegraphics[width=3.5in]{arrio17.png}
\caption{Force information acquired while working with a block of sponge (elastic) and a piece of plasticine (plastic).  Notice the difference in magnitude between the force used with the sponge and the plasticine.}
\label{fig:forceElasticPlastic}
\end{figure}

@@

\comment{These technical contributions} enable us to learn models of sensorimotor contingencies, and then to use these as components to build different machines. This approach enables i) predictions over many steps, ii) learning of plastic and elastic deformation from real data, iii) prediction of forces experienced by the robot, iv) classification of materials from either or both force and visual data, v) prediction of object behaviour after contact by the robot is removed. In the rest of the paper we present related work (Section~\ref{sec:background}); give an overview of the framework (Section~\ref{sec:model_overview}); describe the two component models in detail (Section~\ref{sec:model}); describe how the model parameters are learned from real data (Section~\ref{sec:learning}); report experiments on prediction and classification with elastic and plastic objects (Section~\ref{sec:experiments}); and finish with a short discussion (Section~\ref{sec:discussion}).

@@

Finally, Cretu et al., used growing neural gas networks to learn to predictively track the deformation of objects.  Even though they managed to make predictions about the deformation of the overall shape of the object, under previously unseen sets of forces, their predictions were evaluated only for the next frame.

>>>>

%\begin{figure}[!t]
%\centering\includegraphics[width=3.5in]{arrio17.png}
%\caption{Force information acquired while working with a block of sponge (elastic) and a piece of plasticine (plastic).  Notice the difference in magnitude between the force used with the sponge and the plasticine.}
%\label{fig:forceElasticPlastic}
%\end{figure}

@@

\comment{These technical contributions} enable us to learn models of sensorimotor contingencies, and then to use these as components to build different machines. This approach enables i) predictions over many steps, ii) learning of plastic and elastic deformation from real data, iii) prediction of forces experienced by the robot, iv) classification of materials from either or both force and visual data, v) prediction of object behaviour after contact by the robot is removed. In the rest of the paper we present related work (Section~\ref{sec:background}); give an overview of the framework (Section~\ref{sec:model_overview}); describe the two component models in detail (Section~\ref{sec:model}); describe how the model parameters are learned from real data for the shape prediction model (Section~\ref{sec:learning}) and for the force prediction model (Section~\ref{sec:forces}); report experiments on prediction and classification with elastic and plastic objects (Section~\ref{sec:experiments}); and finish with a short discussion (Section~\ref{sec:discussion}).

@@

Finally, Cretu et al. \cite{Cretu2012}, used growing neural gas networks to learn to predictively track the deformation of objects.  Even though they managed to make predictions about the deformation of the overall shape of the object, under previously unseen sets of forces, their predictions were evaluated only for the next frame.
